\newcommand{\DpositionOneStartYear}{}
\newcommand{\Dmail}{npentrel@gmail.com}
\newcommand{\Dpositions}{jacobsHack! Co-Founder | Advisor  / Co-founder; advisor; and former main-organizer of the hackathon series "jacobsHack!" at Jacobs University  Bremen; sponsored by companies such as Google; Microsoft; and SAP. Gained sponsorship; managed the  20;000 Euro budget; and outreach activities and communication with students before and during the organization  of jacobsHack! 2014/   jacobsHack!/5/2013,Software Engineering Intern  / Part of the Infrastructure Automation team. Aided multiple teams by improving build and test frameworks;  providing API wrappers; and writing scripts. Predominantly worked in Java and Python/   Palantir Technologies/5/2013,Teaching Assistant Python lab; C lab; and General Computer Science  / Prepared and held tutorials as well as taught students both general Computer Science topics and  programming. Graded homework assignments and exams/   Jacobs University Bremen/5/2013,Teaching Assistant for the Career Services Center  / Creating a website; managing web content; and assisting in event organization and social media maintenance.  Database creation and management. Guiding students through employment and university recruitment  processes through individual counseling. Conducting workshops on Application Training and Effective  Presentations with Prezi/   Jacobs University Bremen/5/2013,Software Development Intern  / Part of the Cross Client Onboarding team. Creation of a new onboarding experience for the Skype app on  different platforms predominantly using AngularJS; HTML; and SCSS/   Microsoft/5/2013,Software Engineering Intern  / Part of the Chrome Privacy team. Developing a new User Interface with new functionality for the password  manager within Chrome. Primarily using C++ for the implementation but also C and Objective-C to  implement the counterparts for the respective Operating Systems/   Google/5/2013,Prezi U Ambassador  / Introduced Prezi at Jacobs University Bremen using social media; workshops; competitions; and other  creative and engaging means. Organized a Prezi Hackathon for business and IT students that allowed them  to come up with and implement a feature that can make Prezi more interactive. Furthermore; translated the  software into German within a team of four and represented Prezi at multiple events such as TEDx events/   Prezi/5/2013,Student Assistant for the Admissions Team  / Involvement in representing Jacobs University Bremen at fairs; counseling activities; and school  presentations. Designing official presentations; advertisements; and posters. Database management; social  media maintenance; scheduling and organizing events; writing newsletter articles. Helping in organizing the  Summer Campus Germany; a two-week event organized to students from around the world to experience  university life/   Jacobs University Bremen/5/2013}
\newcommand{\DpositionOneStartMonth}{}
\newcommand{\DfirstName}{Naomi}
\newcommand{\Dtagline}{Student at the University of Oxford}
\newcommand{\Dlinkedin}{https://www.linkedin.com/in/npentrel}
\newcommand{\DpictureUrl}{https://media.licdn.com/mpr/mprx/0_P9cTGtGmw3TMRb9OANIGCn-wexhrmLBO6koi9ufeV38z0dRg5yIb1mPw43Dv0dB-vyoFtH-aI52zuqqO_gQazWtHy52vuqoO6gQ_8tmedxgyu_UB6JnCQg3KUr}
\newcommand{\DpositionOneCompany}{}
\newcommand{\Dcountry}{UK}
\newcommand{\Dcity}{London}
\newcommand{\DfullName}{Naomi Pentrel}
\newcommand{\DlastName}{Pentrel}
\newcommand{\DpositionOneSummary}{}
\newcommand{\DpositionOnetitle}{}
